---
title: "plotly_example.Rmd"
author: "michael.coursera@eipsoftware.com"
date: "November 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exchange rates of British Pound against other currencies.

The line graph below shows the historical exchange rate. on the first of each month, of the British Pound against three other currencies.

+ GBP-USD  British Pound compared against the United States Dollar
+ GBP-EUR  British Pound against the Euro	
+ GBP-CHF  British Pound against the Swiss Franc

Date Great Britian voted for leaving the European Union **23 Jun 2016.**

<br />
<br />

```{r load_library, echo=FALSE, message=FALSE}
library(dplyr)
library(plotly)
xe <- read.csv("xe_rates.csv")

xe <- xe %>% mutate(Month = as.Date(Month, format="%m/%d/%Y"))

#list variables to hold the parameters
font_x <- list(family = "Arial, sans-serif"
			  ,size = 8
			)

axis_x <- list(title = "Month"
			  ,tickFont = font_x
			  ,tickangle = -90
			)

xe_margins <- list(t=100, r=50, b=160, l=140, pad=10)

#plot the graph
xe_plot <- plot_ly(xe, x = ~Month, y = ~GBP.USD, name = "GBP-USD" ,type = 'scatter', mode = 'lines') %>%
		   add_trace(y = ~GBP.EUR, name="GBP-EUR") %>%
		   add_trace(y = ~GBP.CHF, name="GBP-CHF") %>%
		   layout(title = "Exchange rates of British Pound"
				 ,margin = xe_margins
		   	   	 ,xaxis = axis_x
		   	     ,yaxis = list(title ="Exchange Rate")
		   	   	 )

xe_plot
```





***

### R Source Code

<br />
<br />

```{r echo=TRUE, eval=FALSE}
library(dplyr)
library(plotly)
xe <- read.csv("xe_rates.csv")

xe <- xe %>% mutate(Month = as.Date(Month, format="%m/%d/%Y"))

#list variables to hold the parameters
font_x <- list(family = "Arial, sans-serif"
			  ,size = 8
			)

axis_x <- list(title = "Month"
			  ,tickFont = font_x
			  ,tickangle = -90
			)

xe_margins <- list(t=100, r=50, b=160, l=140, pad=10)

#plot the graph
font_x <- list(family = "Arial, sans-serif"
			  ,size = 8
			)

axis_x <- list(title = "Month"
			  ,tickFont = font_x
			  ,tickangle = -90
			)

xe_margins <- list(t=100, r=50, b=160, l=140, pad=10)

xe_plot <- plot_ly(xe, x = ~Month, y = ~GBP.USD, name = "GBP-USD" ,type = 'scatter', mode = 'lines') %>%
		   add_trace(y = ~GBP.EUR, name="GBP-EUR") %>%
		   add_trace(y = ~GBP.CHF, name="GBP-CHF") %>%
		   layout(title = "Exchange rates of British Pound"
				 ,margin = xe_margins
		   	   	 ,xaxis = axis_x
		   	     ,yaxis = list(title ="Exchange Rate")
		   	   	 )

xe_plot
```





***
Source for XE data: [www.x-rates.com](http://www.x-rates.com)